% ----------------------------------------------------------------------------------------------------------------
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate}

\usepackage{amssymb,amsmath}
\usepackage{wrapfig}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
%\usepackage{times}
\usepackage{cite}
\usepackage{url}
\usepackage{booktabs}
%\usepackage{subfigure}
\usepackage{fancybox}
\usepackage{color}
\usepackage{array}
%\usepackage{subfigure}
\usepackage{caption,subcaption}
\usepackage{balance}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{xspace}







\graphicspath{ {../images/} }

% author comments with colors 
\newcommand{\emad}[1]{\textcolor{red}{{\it [Emad: #1]}}}
\newcommand{\alexander}[1]{\textcolor{red}{{\it [Alexander: #1]}}}
\newcommand{\everton}[1]{\textcolor{blue}{{\it [Everton: #1]}}}
\newcommand{\rabe}[1]{\textcolor{blue}{{\it [Rabe: #1]}}}
\newcommand{\todo}[1]{\colorbox{yellow}{\textbf{[#1]}}}

% conclusion box for summarize the research questions
\newcommand{\conclusionbox}[1]{%
       \vspace{2mm}
       \framebox[0.45\textwidth][c]{%
              \parbox[b]{0.42\textwidth}{%
                     {\it #1}
              }
       }
       \vspace{2mm}
}


\newcommand{\conclusion}[1]{%
\begin{center}
	\noindent\thicklines\setlength{\fboxsep}{8pt}\cornersize{0.03}\Ovalbox{\begin{minipage}{3in}\textit{
	\textbf{#1}
}\end{minipage} }
\end{center}
}











\newcommand{\rqi}{\textbf{RQ1. How much self-admitted technical debt gets removed?\\}}
\newcommand{\rqii}{\textbf{RQ2. Who removes self-admitted technical debt? Is it most likely to be self-removed or removed by others?\\}}
\newcommand{\rqiii}{\textbf{RQ3. How long does self-admitted technical debt survive in a project?\\}}
% \newcommand{\rqiii}{\textbf{RQ3. How long does self-admitted technical debt survive in a project?\\}}
\newcommand{\rqiv}{\textbf{RQ4. What activities lead to the removal of self-admitted technical debt?\\}}

\newcommand{\SATD}{self-admitted technical debt\xspace}
\newcommand{\CSATD}{Self-admitted technical debt\xspace}



\begin{document}


\setcopyright{acmcopyright}

% % DOI
% \doi{10.475/123_4}

% % ISBN
% \isbn{123-4567-24-567/08/06}

% %Conference
% \conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

% \acmPrice{\$15.00}


% --- Author Metadata here ---
% \conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{An Empirical Study On the Removal of Self-Admitted Technical Debt}
\numberofauthors{1} 
\author{
%%	\alignauthor 
%	Everton da S. Maldonado\textsuperscript{\S}, Rabe Abdalkareem\textsuperscript{\S}, Emad Shihab\textsuperscript{\S}, Alexander Serebrenik\textsuperscript{\textdagger}\\
%	\affaddr{}
%	\affaddr{\textsuperscript{\S}Dept. Computer Science and Software Engineering, Concordia University, Montreal, Canada}\\
%	% \email{e\_silvam@encs.concordia.ca}
%	% \email{eshihab@cse.concordia.ca}
%%	\alignauthor 
%%	Alexander Serebrenik\\ 
%	\affaddr{\textsuperscript{\textdagger}Eindhoven University of Technology, Eindhoven, The Netherlands}\\
%	\email{\url{{e_silvam,rab_abdu,eshihab}@encs.concordia.ca}, \url{a.serebrenik@tue.nl}}
}

\maketitle
\begin{abstract}
Technical debt refers to the phenomena of taking shortcuts to achieve short term gain at the cost of higher maintenance efforts in the future. Recently, approaches were developed to detect technical debt through code comments, referred to as Self-Admitted Technical debt (SATD). Due to its importance, several studies have focused on the detection of SATD and examined its impact on software quality. However, preliminary findings showed that in some cases SATD may live in a project for a long time, i.e., more than 10 years. These findings clearly show that not all SATD may be regarded as `bad' and some SATD needs to be removed, while other SATD may be fine to take on. Hence, the question becomes - which SATD should be removed?

Therefore, in this paper, we study the removal of SATD. In an empirical study on five open source projects, we examine how much SATD is removed and who removes SATD? We also investigate for how long SATD lives in a project and what activities lead to the removal of SATD? Our findings indicate that, on average, 74.9\% of SATD is removed, that aprox. 54.3\% is self-removed (i.e., removed by the same person that introduced it) and that self-removed SATD is addressed within 18 days, whereas non-self-removed SATD takes 127 days to address, on median.
\end{abstract}

% A category with the (minimum) three required fields
% \category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
% \category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{}

\keywords{Self-Admitted Technical Debt, Source Code Quality, Mining Software Repositories}

\section{Introduction}
\label{sec:introduction}
\input{introduction}

% \section{Motivating Example}
% \label{sec:motivating_example}
% \input{motivation}

\section{Case Study Setup}
\label{sec:approach}
\input{approach}

\section{Case study Results}
\label{sec:case_study_results}
\input{results}

\section{Discussion}
\label{sec:discussion}
\input{discussion}

\section{Related Work}
\label{sec:related_work}
\input{related_work}


\section{Threats to Validity}
\label{sec:threats_to_validity}
\input{threats_to_validity}

\section{Conclusion and Future work}
\label{sec:conclusion}
\input{conclusion}

\bibliographystyle{abbrv}
\balance
\bibliography{bibliography}  
\end{document}